P4IRS: An Intermediate Representation and Compiler for Parallel and Performance-Portable Particle Simulations

### 2024-07-04 sage_latex_template/manuscript.tex
minor
Signed-off-by: Rafael Ravedutti <rafael.r.ravedutti@fau.de>

\bibitem[Ravedutti Lucio Machado~R et al.(2023)]{mdbench1}
Rafael Ravedutti Lucio~Machado, Jan Eitzinger, Harald K{\"o}stler, and Gerhard
  Wellein.
\newblock MD-Bench: A generic proxy-app toolbox for state-of-the-art molecular
  dynamics algorithms.
\newblock In Roman Wyrzykowski, Jack Dongarra, Ewa Deelman, and Konrad
  Karczewski, editors, {\em Parallel Processing and Applied Mathematics}, pages
  321--332, Cham, 2023. Springer International Publishing.

\bibitem[Ravedutti Lucio Machado~R et al.(2023)b]{mdbench2}
Rafael {Ravedutti Lucio Machado}, Jan Eitzinger, Jan Laukemann, Georg Hager,
  Harald Köstler, and Gerhard Wellein.
\newblock MD-Bench: A performance-focused prototyping harness for
  state-of-the-art short-range molecular dynamics algorithms.
\newblock {\em Future Generation Computer Systems}, 149:25--38, 2023.

>>>>

\bibitem[Ravedutti Lucio Machado~R et al.(2023a)]{mdbench1}
Rafael Ravedutti Lucio~Machado, Jan Eitzinger, Harald K{\"o}stler, and Gerhard
  Wellein.
\newblock MD-Bench: A generic proxy-app toolbox for state-of-the-art molecular
  dynamics algorithms.
\newblock In Roman Wyrzykowski, Jack Dongarra, Ewa Deelman, and Konrad
  Karczewski, editors, {\em Parallel Processing and Applied Mathematics}, pages
  321--332, Cham, 2023. Springer International Publishing.

\bibitem[Ravedutti Lucio Machado~R et al.(2023b)]{mdbench2}
Rafael Ravedutti Lucio Machado, Jan Eitzinger, Jan Laukemann, Georg Hager,
  Harald Köstler, and Gerhard Wellein.
\newblock MD-Bench: A performance-focused prototyping harness for
  state-of-the-art short-range molecular dynamics algorithms.
\newblock {\em Future Generation Computer Systems}, 149:25--38, 2023.
